SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-28 scipy-1.0/ckdtree.tex
Update ckdtree.tex (#1)
Update ckdtree.tex
avoid colloquial style

In 2013, the time complexity of the $k$-nearest neighbor search from
\texttt{cKDTree.query} was approximately loglinear \cite{knn-jake},
consistent with its formal description \cite{kdtree-search-algo}.
Since then, we've enhanced \texttt{cKDTree.query} by reimplementing it in
C++, removing memory leaks, and allowing release of the global interpreter lock (GIL) so that
multiple threads may be used\cite{gh-4374}. This generally improved
performance on any given problem (Figure~\ref{fig:asvbench})
while preserving the asymptotic complexity.
%(Figure~\ref{fig:knn-complexity}).

In 2015, SciPy added the \texttt{sparse\_distance\_matrix} routine for generating 
approximate sparse distance matrices between \texttt{KDTree} objects by ignoring 
all distances that exceed a user-provided value. Also, this routine is not 
limited to the conventional L2 (Euclidean) norm but supports any Minkowski 
$p$-norm between 1 and infinity. By default, the returned data structure is a
Dictionary Of Keys (DOK) based sparse matrix, which is very efficient for matrix 
construction. This hashing approach to sparse matrix assembly can be 7 times 
faster than constructing with CSR format
\cite{10.1007/978-3-540-75755-9_107}, and the C++ level sparse matrix construction 
releases the Python GIL for increased performance. Once the matrix is constructed, 
distance value retrieval has an amortized constant time complexity 
\cite{Cormen:2001:IA:580470}, and the DOK structure can be efficiently converted 
to a CSR, CSC, or COO matrix to allow for 
speedy arithmetic operations.

>>>>

In 2013, the time complexity of the $k$-nearest neighbor search from
\texttt{cKDTree.query} was approximately loglinear \cite{knn-jake},
consistent with its formal description \cite{kdtree-search-algo}.
Since then, we have enhanced \texttt{cKDTree.query} by reimplementing it in
C++, removing memory leaks, and allowing release of the global interpreter lock (GIL) so that
multiple threads may be used\cite{gh-4374}. This generally improved
performance on any given problem (Figure~\ref{fig:asvbench})
while preserving the asymptotic complexity.
%(Figure~\ref{fig:knn-complexity}).

In 2015, SciPy added the \texttt{sparse\_distance\_matrix} routine for generating
approximate sparse distance matrices between \texttt{KDTree} objects by ignoring
all distances that exceed a user-provided value. This routine is not
limited to the conventional L2 (Euclidean) norm but supports any Minkowski
$p$-norm between 1 and infinity. By default, the returned data structure is a
Dictionary Of Keys (DOK) based sparse matrix, which is very efficient for matrix
construction. This hashing approach to sparse matrix assembly can be 7 times
faster than constructing with CSR format
\cite{10.1007/978-3-540-75755-9_107}, and the C++ level sparse matrix construction
releases the Python GIL for increased performance. Once the matrix is constructed,
distance value retrieval has an amortized constant time complexity
\cite{Cormen:2001:IA:580470}, and the DOK structure can be efficiently converted
to a CSR, CSC, or COO matrix to allow for
speedy arithmetic operations.

### 2019-07-28 scipy-1.0/paper.tex
avoid colloquial style

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (\texttt{@}) operator.
We've added \texttt{scipy.sparse.norm} and
\texttt{scipy.sparse.random} for computing sparse matrix norms and drawing
random variates from arbitrary distributions, respectively. Also, we've made a
concerted effort to bring the \texttt{scipy.sparse} API into line with the
equivalent NumPy API where possible.

>>>>

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (\texttt{@}) operator.
We have added \texttt{scipy.sparse.norm} and
\texttt{scipy.sparse.random} for computing sparse matrix norms and drawing
random variates from arbitrary distributions, respectively. Also, we have made a
concerted effort to bring the \texttt{scipy.sparse} API into line with the
equivalent NumPy API where possible.
